Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-25 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with any composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower. Eventually, the collection of consisting states collapses
to the singleton set~$\left\{ \rho\right\} $ as the intervals becomes
the infinitely precise intervals~$\mathscr{I}_{\infty}$. This fact
is a weak version of Gleason's theorem because we only consider composited
QIVPMs $\iota\circ\mu_{\rho}^{\mathrm{B}}$ instead of general QIVPMs~$\bar{\mu}$.
To precisely state this result, we need to introduce the norm of pure
states and operators. The norm of a pure state~$\ket{\psi}$ is defined
as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Similarly,
given any Hermitian operator~$A$, we consider the usual operator
norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
Then, a weak version of Gleason's theorem can be stated as follow.

>>>>

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with any composited QIVPM $\iota\circ\mu_{\rho}^{\mathrm{B}}$.
Moreover, the collection of states consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower. Eventually, the collection of consisting states collapses
to the singleton set~$\left\{ \rho\right\} $ as the intervals become
the infinitely precise intervals~$\mathscr{I}_{\infty}$. This fact
is a weak version of Gleason's theorem because we only consider composited
QIVPMs $\iota\circ\mu_{\rho}^{\mathrm{B}}$ instead of general QIVPMs~$\bar{\mu}$.
To precisely state this result, we need to introduce the norm of pure
states and operators. The norm of a pure state~$\ket{\psi}$ is defined
as usual $\left\Vert \psi\right\Vert =\sqrt{\ip{\psi}{\psi}}$. Similarly,
given any Hermitian operator~$A$, we consider the usual operator
norm $\left\Vert A\right\Vert =\max_{\left\Vert \psi\right\Vert =1}\left\Vert A\ket{\psi}\right\Vert $,
which is also known as $2$-norm or spectral norm~\citep{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996,Foucart2012}.
Then, a weak version of Gleason's theorem can be stated as follow.
